---
title: "R Notebook"
output: html_notebook
---


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

```{r load some data}

url <- "https://data.boston.gov/dataset/f9f57091-92f3-463a-8f1c-93e46361296d/resource/36fcf981-e414-4891-93ea-f5905cec46fc/download/streetconstruction.csv"
bosdata <- read.csv(url,stringsAsFactors = FALSE)

```
```{r wrangling and beautifying}
#Neighborhood as factors
library(lubridate)
bosdata$Neighborhood <- factor(bosdata$Neighborhood)
#strinds that looks like dates as dates
bosdata$ExpirationDate <- mdy_hm(bosdata$ExpirationDate)
bosdata$EstimatedCompletionDate <- mdy_hm(bosdata$EstimatedCompletionDate)
#Making full addresses
bosdata$fullAddress <- paste(bosdata$Address1,bosdata$Street,"BOSTON,MA",' ')
#Geocoding those addresses
library(ggmap)
bosdata$lat <- ggmap::geocode(bosdata$fullAddress)$lat
bosdata$lng <- ggmap::geocode(bosdata$fullAddress)$lon
save(bosdata,file="./data/bosdata.Rda")

```
```{r}
# now lets create a map

bosmap <-leaflet() %>% 
        addTiles() %>%
        setView(lng = -71.0589, lat = 42.3601, zoom = 12) %>%
        addMarkers(lat=bosdata$lat,lng=bosdata$lng,popup=bosdata$ProjectCategory)
bosmap  
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
